A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-02-20 papers/execution-model/model.tex
parenthetical bibrefs

\section{Related Work}
\label{sec:related work}
The inability to access external data sources limits the potential of smart contracts. Oracles \cite{oracle-patterns,call-action-oracle,oracles-study} can help overcome this limitation by providing a bridge between the outside sources and the blockchain network. A blockchain oracle is used to provide external data to smart contracts. Several researches have been done to provide oracle solutions for blockchain. The work in \cite{blockchain-oracles} proposes a framework to explain blockchain oracles and various key aspects of oracles. This framework aims to provide developers with a guide for incorporating oracles into blockchain-based applications. Practically, the decentralized oracle network Chainlink \cite{chainlink-whitepaper} is being developed to provide reliable, tamper-proof input for smart contracts on any blockchain. For a specific application, a system called Town Crier \cite{town-crier} provides an authenticated data feed, sourced from HTTPS-enabled data websites, for smart contracts on Ethereum. The authors in \cite{oracle-real-value} construct an oracle that can estimate the value of a real quantity, such as $R$. 
For application to prediction markets, there are Truthcoin system \cite{truthcoin-whitepaper} and Astraea, a trustless decentralized oracle \cite{astraea}.

The main problems with using a blockchain oracle are the untrusted data provided maliciously or inaccurately \cite{trustworthy}. The researchers in \cite{reliable-oracle} propose an oracle equipped with verification and disputation mechanisms. Similarly, researchers in \cite{reliablity-oracles} provide a framework for performing reliability analysis of various blockchain oracle platforms. Closely following our work, the authors in \cite{interact-coq} present a model-executable specification of smart-contract execution in Coq. Their formalizations target Ethereum and Tezos.

>>>>

\section{Related Work}
\label{sec:related work}
The inability to access external data sources limits the potential of
smart contracts. Oracles
\cite{oracle-patterns,call-action-oracle,oracles-study} can help
overcome this limitation by providing a bridge between the outside
sources and the blockchain network. A blockchain oracle is used to
provide external data to smart contracts. Several researches have been
done to provide oracle solutions for blockchain. Adler et al
\cite{blockchain-oracles} propose a framework to explain blockchain
oracles and various key aspects of oracles. This framework aims to
provide developers with a guide for incorporating oracles into
blockchain-based applications. Practically, the decentralized oracle
network Chainlink \cite{chainlink-whitepaper} is being developed to
provide reliable, tamper-proof input for smart contracts on any
blockchain. For a specific application, a system called Town Crier
\cite{town-crier} provides an authenticated data feed, sourced from
HTTPS-enabled data websites, for smart contracts on Ethereum. George
and Lesaege \cite{oracle-real-value} construct an oracle that can
estimate the value of a real quantity, such as $R$.  
For application to prediction markets, there are Truthcoin system
\cite{truthcoin-whitepaper} and Astraea, a trustless decentralized
oracle \cite{astraea}.

The main problems with using a blockchain oracle are the untrusted
data provided maliciously or inaccurately \cite{trustworthy}. Ma at el
\cite{reliable-oracle} propose an oracle equipped with 
verification and disputation mechanisms. Similarly, Lo et al
\cite{reliablity-oracles} provide a framework for performing
reliability analysis of various blockchain oracle platforms. Closely
following our work, Nielsen and Spitters \cite{interact-coq} present a
model-executable specification of smart-contract execution in
Coq. Their formalizations target Ethereum and Tezos.
